---
title: "How to use pmfdR"
author: "Marcelo Perlin"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How to use pmfdR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Package `pmfdR` provides access to all material from my book **Processing and Modelling Financial Data with R**. You can find more details about it [here](https://sites.google.com/view/pmfdr/home).

With `pmfdR` you can:

1) Download data and code with function `pmfdR_download.code.and.data`
2) Build exercises with function `pmfdR_build.exercise`

## Downloading code and data

All the R code from the book is publicly available in [github](https://github.com/msperlin/pmfdR-en-code_data/). Function `pmfdR_download.code.and.data` will download a zip file from the repository and unzip it at specified folder. Have a look in its usage:

```{r, eval=FALSE}
if (!require(pmfdR)){
  install.packages('pmfdR')
  library(pmfdR)
} 

my.lan <- 'en' # language of code and data ('en' or 'pt-br')

# dl may take some time (around 60 mb)
pmfdR_download.code.and.data(lan = my.lan)

dir.out <- 'pmfdR-en-code_data-master'

# list R code
list.files(dir.out, pattern = '*.R')
list.files(paste0(dir.out,'/data'))
```

## Building exercises

All exercises from the book are based on package `exams`. This means that every reader will have a different version of the exercise, with different values and correct answer. I've written extensively about the positive aspects of using `exams`. You can find the full post [here](https://msperlin.github.io/2017-01-30-Exams-with-dynamic-content/)

You can create your custom exercise file using function `pmfdR_build.exercise`. Give it a try, just copy and paste the following chunk of code in your R prompt.

```{r, eval=FALSE}
if (!require(pmfdR)){
  install.packages('pmfdR')
  library(pmfdR)
} 

my.lan <- 'en' # language of exercises
my.exercise.folder <- 'pmfdR-exercises' # name of folder with exercises files (will download from github)
my.pdf.folder <- 'PdfOut' # name of folder to place pdf file and answer sheet

pmfdR_build.exercise(lan = my.lan,
                     exercise.folder = my.exercise.folder, 
                     pdf.folder = my.pdf.folder)

list.files(my.pdf.folder)
```

